---
title: "Indian Geo-Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/Desktop/DAV/India_Geodata/india-census/")

library(tidyverse)
library(rgdal)        
library(ggplot2)
library(wesanderson)
library(RColorBrewer)
library(ggmap)

```

# Description:

This data visualization task comprises the following efforts: <br />
* Visualizing road, railways and water networks of India <br />
* Visualizing population density based on the Census-2011 <br />
* Visualizing locations of McDonald's franchises across India <br />

The overall aim was to work with geodata files from across the web- most of the files available here have been compiled from various sources and put together a meaningful set of visualizations. I am inspired to visualize other important data (like female literacy, access to healthcare, banking etc) from the indian census through these amazing tools post this assignment.  <br />

I downloaded the following shapefiles from ArcGIS. <br />
* IND_adm0 = contains the boundaries of india. <br />
* IND_adm1 = used for state-wise data. <br />
* IND_adm2 = used for district-wise data. <br />
* IND_rds = Indian road-networks. <br />
* IND_rrd = Indian railway networks <br />

Census 2011 data was downloaded separately from Kaggle Datasets. <br />
McDonalds data was exported as geoJSON from overpassturbo by querying OpenStreetMaps. Converted it into a shapefile and plotted it along the shapefiles from arcGIS. <br />

# Indian Road Networks: 
```{r}
maindir="~/Desktop/DAV/India_Geodata"
paste(maindir,'/IND_adm',sep='')
ind_adm_0= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm0')
ind_adm_1= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm1')
ind_adm_2= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm2')
ind_adm_3= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm3')
ind_rds= readOGR(paste(maindir,'/IND_rds',sep=''),'IND_roads')

ggplot() + geom_polygon(data=ind_adm_0,aes(x=long, y=lat,group=group), fill='white', col=rgb(0,0,0.3,alpha = 0.3)) + 
  geom_path(data=ind_rds, aes(x=long, y=lat, group=group), col='red') + 
 labs(title= 'India- Road Networks', x='',y='') +
  coord_fixed() + theme_void()

```

# Indian Railway Network 
```{r}

ind_rwy= readOGR(paste(maindir,'/IND_rrd',sep=''),'IND_rails')
ind_adm_0= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm0')
ggplot() + geom_polygon(data=ind_adm_0,aes(x=long, y=lat,group=group), fill='white', col=rgb(0,0,0.3,alpha = 0.3)) + 
  geom_path(data=ind_rwy, aes(x=long, y=lat, group=group), col='green') + 
  coord_fixed() + 
  labs(title= 'Indian Railway Network', x='', y='')
```

# Indian Water Lines and Water Areas 
```{r}

ind_waterlines=readOGR(paste(maindir,'/IND_wat',sep=''),'IND_water_lines_dcw')
ind_waterareas=readOGR(paste(maindir,'/IND_wat',sep=''),'IND_water_areas_dcw')

ggplot() + geom_polygon(data=ind_adm_0,aes(x=long, y=lat,group=group), fill='white', col=rgb(0,0,0.3,alpha = 0.3)) + 
  geom_path(data=ind_waterlines, aes(x=long, y=lat,group=group), col=rgb(0,0,0.5,alpha=0.5)) + 
  labs(title= 'Indian Water Line and Areas', x='', y='') +
     coord_fixed() + 
    theme_void()
  
```

# Ppopulation Data from Census-2011 
#### Downloaded from Kaggle. 

```{r}
popdata= read.csv('india-districts-census-2011.csv', header=TRUE, sep=',')
head(popdata)
```

```{r}
popdata=popdata[,1:6]
popdata=popdata[,-1]
states= unique(popdata[,1])
districts= unique(popdata[,2])

```


```{r}
maindir="~/Desktop/DAV/India_Geodata"
ind_adm_2= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm2')
ind_df= fortify(ind_adm_2, region = "NAME_2")

head(ind_df)
```
#### Merging Data

```{r}
merged_data = merge(ind_df,popdata, by.x='id',by.y='District.name')
head(merged_data)
```

# Generating Choropeth : based on population density. 
```{r}
# plotting again 
Total= sum(popdata$Population)
ind_adm_0= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm0')
ggplot() + 
  geom_polygon(data=ind_adm_0,aes(x=long, y=lat,group=group), fill='white', col=rgb(0,0,0.3,alpha = 0.3)) +
  geom_polygon(data=merged_data, aes(x = long, y = lat, group = group, color= merged_data$Population), size = 0.25)  + 
  coord_fixed() +
  labs(title=' Indian population data', x='',y='') +
  theme_void()

#ggsave("india_population_data.png")
```
# McDonalds in India 
## __Where are the McDonalds in India?__

Useful tip: use [link](http://bboxfinder.com/) to find bounding box coordinates for your region of interest. <br /> 

```{r}
# Trying to plot McDs in india with data exported from overpassturbo and OSM 

#boundaries: 
maindir="~/Desktop/DAV/India_Geodata"
ind_adm_0= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm0')
ind_adm_1= readOGR(paste(maindir,'/IND_adm',sep=''),'IND_adm1')


#getting mcd locations from shapefile
ind_mcd= readOGR(paste(maindir,'/mcd_india_shpfile',sep=''),'export')

#I notice there are McDs here that lie outside indian boundary. So I clip the data:
bbox(ind_adm_0)
mcd_clipped= ind_mcd[ind_adm_0,]

#Plotting with clipped data
plot(ind_adm_0,main='McDonalds Locations in India')
plot(ind_adm_1,main='McDonalds Locations in India',add=TRUE)
plot(mcd_clipped, col=rgb(0.8,0,0),main='McDonalds Locations in India',add=TRUE)

# Plotting the points with buffer: 
library(rgeos)
buf = gBuffer(mcd_clipped, width = 500, byid = TRUE) 

#converting spatialpointsdataframe to dataframe 
mcd_points_df = data.frame(mcd_clipped)

#trying to plot
#ggplot() + 
  #geom_polygon(data=ind_adm_0,aes(x=long,y=lat,group=group), fill='white',color='blue') +
  #geom_polygon(data=buf,aes(x = long, y = lat, group = group), fill = "#F9DA95", color = "white", size = 0.25, alpha = 0.4) 
  #geom_point(data=mcd_points_df, aes(x= coords.x1 ,y= coords.x2), color='red',size=0.25)+
#labs(title='McDonalds Locations in India',x='',y='') +
 # coord_fixed()
```


